\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

\name{Oğuzhan}{Akıncı}

\address{Ankara}{Turkey}
\phone[mobile]{+90~(542)80231~41}
\email{oguzzhanakinci@gmail.com}
\social[linkedin]{oguzhanaknc}
\social[github]{oguzhanaknc}

\begin{document}
\makecvtitle

\section{Profile}
\cvitem{}{Hi, my name is Oğuzhan and I am 23 years old. I am a student in my final year of Statistics and Computer Science at Karadeniz Technical University. During the pandemic and after, I had the opportunity to apply my theoretical knowledge by pausing my studies. I gained the ability to produce work of military quality in a minimal amount of time by working in the defense industry.}

\section{Education}
\cventry{2017--2023}{Bachelor's Degree}{Karadeniz Technical University}{Trabzon, Turkey}{\textit{GPA: 3.2/4.0}}{Department: Computer Science and Statistics}
\cventry{2013--2017}{High School}{Ankara Anatolian High School}{Ankara, Turkey}{\textit{Diploma Degree: 85/100}}{}

\section{Experience}
\cventry{2021--2022}{Software Developer}{Selvi Technology}{Ankara, Turkey}{}{
\begin{itemize}
\item Backend of a web-based unmanned aerial vehicle control system using Python and Flask.
\item Developed command control interface using ReactJs, HTML5 and CSS3.
\item Developed geographic information systems for border security systems using React.
\item Programming of UAV flight dynamics.
\end{itemize}
}

\section{Projects}
\cvitem{Illusion}{A low-level custom game engine prototype using C++ and Vulkan.}

\section{Skills}
\cvitem{Programming Languages}{C#, C++, Python}
\cvitem{Game Development}{Unity, SMFL, OpenGL, Vulkan,}
\cvitem{Database}{MySQL, PostgreSQL, MongoDB}
\cvitem{Tools and Technologies}{Git, Docker, RESTful APIs, Agile/Scrum}

\section{Language Skills}
\cvitemwithcomment{Turkish}{Native}{}
\cvitemwithcomment{English}{Advanced}{}

\section{Certificates & Licenses}
\cvlistitem{Deep Learning Specialization}
\cvlistitem{ISO/IEC 27001 Information Security}
\cvlistitem{ISO/IEC 9001:2015 Quality Management}

\section{Volunteer Works}
\cvitem{Community Involvement}{Actively involved in the Google Developer Group Trabzon as a member of the management team, organizing events and workshops to promote technology and community involvement.}
\cvitem{high school software club}{Taught basic programming skills to high school students in Ankara, Turkey}

\end{document}